### 2013-12-16 paper/paper.tex
blach

\usepackage{epigraph}

@@

\usepackage{etoolbox}

\makeatletter
\patchcmd{\epigraph}{\@epitext{#1}}{\itshape\@epitext{#1}}{}{}
\makeatother\usepackage{algorithm}
\usepackage{multirow}
\usepackage{algpseudocode}
\begin{document}
% generates the title
\begin{titlepage}
\begin{center}

@@

\begin{abstract}
On a given day, a large open-source Git Repository likely receives many pull requests, plenty of which are submitted by “untrusted” public members who have yet to contribute to the repository. With so much information to look up and code to test for managers of the repository, we have developed a method to extract metadata about commits and their messages, analyze this data using machine learning techniques, and determine which commits are suspect for introducing new bug(s). The accuracy of our classification method is verified using a number of open-source git repositories, including jedit, jquery, scala, and git itself. Our ensemble classifier correctly predicts bugginess of commits between 70 and 90\% of the time, outperforming the baseline of random weighted guessing by roughly 15 to 25\%. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about suspect commits and also seeks to inform contributors in ways to improve their commit structure to make their commits less suspect.
\end{abstract}

@@

In this paper, we discuss our development of a model which attempts to predict the bugginess of commits submitted to a repository using machine-learning techniques. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about which commits are most likely to be buggy. The next section frames this project with the related work of others. Section \ref{approach} discusses our approach in developing our model including data sources, feature selection, and algorithm development. Section \ref{results} discusses the refinement of the model, presents our results, and discusses our methodology for validation of our results. Section \ref{threats} discusses shortcomings, threats to validity, and future work, and section \ref{conclude} concludes our paper.

\section{Related Work}
Using version control system history to aid the development process is not a new idea;  the wealth of data that repositories store makes them very attractive artifacts to researchers who want to understand and improve the ways in which code is written.  In the last ten years a good deal of work has gone into trying to use repository data to make various aspects of the development process easier [CITE3]. In the early 2000s Zimmerman et al [CITE1] and Ying [CITE2] developed systems to mine version history to make suggestions on potential locations to make changes based on recent alterations to versioned files. Their results were very interesting, reliably finding associations between sections of code and between code and documentation.

A common goal in many projects involving software repositories is attempting to predict the bugginess of future code using some set of metrics. A wide variety of metrics have been researched, including code churn [6], association of changed files, distance between team members [CITE7], and commit size[CITE8]. Recent research has also been done to analyze the accuracy of predicting one repository’s future defects using a different repository’s past history [CITE12].   Work has also been done on analyzing characteristics of bugs and bug fixes[CITE9] [CITE10]

There has also been some work in attempting to automatically infer which past commit introduced a bug.  Originally described in [CITE], the SZZ algorithm uses keywords to find bug fixes, and then uses the version system’s blame feature to find which commits last touched the code this bug fix attempted to fix.  Future improvements were also made by [CITE], which we discuss in detail later.

Some work has also been done by this group at attempting to use machine learning techniques to predict the bugginess of future commits.  Our work differs from theirs in several ways, namely that their work focuses much more heavily on analysis of committed code, which we generally ignore in favor of the attributes and message of a commit.    
\section{Approach}
\label{approach}
\subsection{Mining Git Repositories}
We mined eight open-source repositories hosted on Github.com for features to serve as our testing data sets ; these can be seen in Table \ref{tab:repos}. The repositories are quite varied; they range in size from around 2000-30000 commits and in age from roughly 3-13 years. The repositories also vary considerably in their goals — they include a programming language, a versioning control system, and a nuclear fuel cycle simulator. We extracted two sets of features about commits from each repository: commit attributes and message attributes. Commit attributes are information about a commit excluding actual analysis of the code or the commit message. Examples of commit attributes we extracted are the number of lines added, the number of lines removed, the contributor, the length of the comment, the day of the week of the commit, and the number of files altered. The commit message attributes we selected are the frequency of words, grammatical correctness, and readability and stylistic metrics of the message. We used the Kincaid metric for readability [CITE], diction, a unix command line tool, to quantify style (triteness, over-wordiness) [CITE], and Queequeg to test the degree of grammatical correctness [CITE] for each commit message. Our analysis of the commit messages assumes they are written in English. A complete list of attributes examined can be found in Table [CITE].

\subsection{Automatically Classifying Past Commits}
To create a classification model from these features, we require a ground truth about whether or not each commit was bug inducing. We used a modified version of the SZZ algorithm from [CITE] to determine the set of commits for each repository that were bug inducing. This technique works by first identifying the set of commits in the repository which are bug fixes. Our modification of the algorithm accomplishes this with an analysis of the commit message looking either for words such as “bug” or “fix” or for strings of numbers and letters that appear to be bug-tracking numbers. After defining this set of bug fix commits, we process each commit individually, identifying sections of source code, called hunks, that the commit altered. For each hunk, we then flag as bug-inducing the most-recent commit before the bug fix commit which altered that hunk of code. This analysis is conducted using an annotation graph search [CITE]. Obviously, this heuristic is imperfect; it depends on bug fix commits being atomic and on bugs being discovered and fixed immediately after their introduction. However, as ASDFSDAF et. al showed in [CITE], this technique tends to work well in practice, as their study using actual developers to confirm bugginess found only a 4-5\% rate of false positives. This algorithm works well in practice and serves as a good estimation for which commits are bug inducing, so we adopted it.

\subsection{Machine Learning Algorithms}
With features extracted and a bugginess classification in hand for each commit for our selected repositories, we have the input prepared for constructing, training, and validating a machine-learning algorithm. After some experimentation with individual classifiers, the method we selected to predict bugginess is an ensemble classifier, which aggregates the outputs of several machine-learning algorithms (see Table CITE (listing ML algorithms and their parameters). Ensemble classifiers generally provide more accurate and consistent results than a single classifier because (assuming the individual classifiers are searching different parts of the hypothesis space) the likelihood of a majority of classifiers being wrong is less likely than a single classifier being incorrect. An added benefit of using an ensemble classifier is it easily allows the user to specify a confidence value for classifying commits as buggy; the more classifiers in agreement, the higher the confidence.  Unless otherwise stated our results take the simple majority of the classifications returned.

The simple, obvious solution would be to classify a pull request clean if all commits in it are clean, otherwise buggy.  This seems to be too drastic a measure however, due to these “oops” commits; any method for classifying requests should take into account that buggy commits in a pull request can potentially contain the associated bug fix in the same request.  We propose a variation on the SZZ algorithm to handle this possibility.  All commits are initially given a label using our ensemble classifier.  For a buggy commit in the pull request, we take every hunk from the commit and look forward in time for a clean commit with that hunk.  Finding a hunk in a clean commit would imply that whatever bug originally existed has been fixed.  If all the buggy hunks have corresponding clean hunks later in the pull request, or if the number of unpaired buggy hunks is below some threshold, the pull request is accepted as clean.  Unfortunately due to time constraints we were not able to test the effectiveness of this method.

@@

The features we chose to represent our commits are fairly simple ones; of the commit attribute data we use, only the day of the week required any computation.  Most of these attributes are presented to the user by git when they make a commit.  We did some initial testing with a decision tree classifier, inspecting changes in results while testing different subsets of features.  We also manually kept track of which features were pruned from the tree, which indicates they are less informative.   We concluded time and date commit data is not very informative for the open source projects we chose to study.  Year and Month are too large to contain much signal, and day of month and minute are too specific.  Because Hour is not stored in local time and the generally distributed nature of these projects, we did not find Hour to be an informative feature.  It is possible that these features could be more valuable in a highly centralized development structure, where there is extra knowledge of development schedules, but without any additional knowledge, we decided to ignore specific time-date data.

\subsection{Testing Methodology}

To test the effectiveness of our feature selection, we mined features from eight open source repositories.  We attempted to choose projects with different life spans and applications to make our results more generalizable.  The list of projects mined, their number of commits, and the percentage of those commits we found to be buggy are in table \ref{tab:repos}.  
\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |}
    \hline
    Repository & Startdate & $\#$  Commits & $\#$ Buggy  Commits & \% Buggy \\ \hline
    one     & June 2008   &   8179 & 2744 & 33.6 \\ \hline
    cyclus & March 2010 &  2162 & 1071 & 49.5 \\ \hline
    git        & April 2005    &   28788 & 10682 & 37.1 \\ \hline
    jedit & Sept 1998 &  6890 & 3190 & 46.3 \\ \hline
    jquery     & March 2006   &   5608 & 3074 & 54.8 \\ \hline
    puppet & April 2005 &  12174 & 4812 & 39.5 \\ \hline
    scala     & Feb 2003   &   20398 & 9584 & 47.0 \\ \hline
    scipy & Feb 2001 &  10035 & 3252 & 32.4 \\ \hline        	
    \end{tabular}
\end{center}\caption{Mined Repositories}
\label{tab:repos}
\end{table}

 For each repository we mined, we took the year of 2013, regardless of its size, to be our test set.  The reasoning behind this is that in practice, users will want to classify new commits as they come in, and the most recent year of commits were the best fit of the data we had. Notice due to the way our heuristic works (start at a bug fix and work back) our test set is likely to contain more false negatives because the bug fixes have potentially not been written yet.  However, in practice this will also be the case, so we feel this should not unreasonably skew our results.

 \begin{figure}
\centering
	\includegraphics[width=0.75\textwidth]{images/history}
\caption{Testing and Training Sets}
\label{git_comp}

For training data, we took commits from the final day of 2012 back six months, one year, two years, and to the start of the repository.  The goal here is to see how our results change with more data to train on (and potentially overfit to).  Tables \ref{tab:size} and \ref{tab:buggy} show the size and percentage of commits which are buggy respectively.  Notice as time increases, the percentage of buggy commits increases (excepting scala all time).  This seems to be an artifact of our heuristic; older bugs are more likely to have associated bug fixes, and so are more likely to be found by our method.  Without having the actual distribution of buggy commits, we can make no assumptions about its trend over time.

	\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |c|}
    \hline

Repo & Test Set & 6Mo Train  & 1 Yr Train   & 2 Yr Train & All Train \\ \hline

one &  2304  &  1190 &  2423 & 4367  &  5874 \\ \hline
cyclus & 546  & 389  & 1231  & 1524  & 1616 \\ \hline
git & 2916  & 1369  & 2630  & 5129  & 25869 \\ \hline
jedit & 165  & 301  & 760  & 1401  & 6725 \\ \hline
jquery & 898  & 592  & 925  & 1934  & 4695 \\ \hline
puppet & 2195  & 980  & 2130  & 3854  & 9979 \\ \hline
scala & 1752  & 1347  & 2983  & 5080  & 18644 \\ \hline
scipy & 1873  & 546  & 1130  & 1786  & 8162 \\ \hline

\end{tabular}
\end{center}\caption{Size of Training and Test Sets}
\label{tab:size}
\end{table}

	\begin{table}[h]
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |c|}
    \hline

Repo & Test Set & 6Mo Train  & 1 Yr Train   & 2 Yr Train & All Train \\ \hline

one  & 23.1 & 26.4 & 30.2 & 35.4 & 37.7 \\ \hline 
cyclus  & 30.6 & 44.4 & 50.6 & 54.9 & 55.9 \\ \hline 
git  & 13.9 & 22.1 & 22.5 & 23.4 & 39.7 \\ \hline
jedit  & 6.7 & 13.9 & 24.7 & 23.1 & 47.3 \\ \hline
jquery  & 35.7 & 43.2 & 46.6 & 53.9 & 58.6 \\ \hline 
puppet  & 18.7 & 20.0 & 26.1 & 29.1 & 44.1 \\ \hline 
scala  & 27.2 & 45.3 & 48.8 & 50.3 & 48.9 \\ \hline 
scipy  & 18.8 & 23.6 & 23.6 & 24.7 & 35.5 \\ \hline
\end{tabular}
\end{center}\caption{Percent Bugginess of Training and Test Sets}
\label{tab:buggy}
\end{table}

%\begin{figure}
  %  \centerline{
%        \subfigure[Git]{%
%            \includegraphics[width=0.4\textwidth,height=.3\textwidth]{images/perc_buggy_git}
%        }%
   %     \subfigure[Puppet]{%
      %     \includegraphics[width=0.4\textwidth,height=.3\textwidth]{images/perc_buggy_puppet}
   %     }
   %     \subfigure[Scala]{%
   %         \includegraphics[width=0.4\textwidth,height=.3\textwidth]{}
      %  }%
 %}
% \caption{Percent Buggy Commits over Time}
%\end{figure}

\begin{figure}[H]%
\centering
\subfloat[Git]{\includegraphics[width=0.5\textwidth]{images/perc_buggy_git}}\hfill%
\subfloat[Puppet]{\includegraphics[width=0.5\textwidth]{images/perc_buggy_puppet}}
\caption{Percent Buggy Commits over Time}
\end{figure}

To compare our features against some baseline, we created a “random weighted coin” classifier which calculated the percent buggy in a training set, and used this percentage as the weight on a random buggy/clean coin for each test instance.  We feel this represents a better floor against which to compare our results than simply using a fair coin. All discussion of random coin results are the average of 100 trials. To compare the effectiveness of attribute and message features, we also trained classifiers using only attribute features, only message features, and both sets of features.

@@

 \begin{figure}
\centering
	\includegraphics[width=1.0\textwidth,height=.5\textwidth]{images/learner_comp}
\caption{Comparison of Feature Results - 1 Year}
\label{git_comp}

\end{figure}
Figure \ref{git_comp} contains our accuracy results of every mined repository using one year of training data.  Results for random weighted coin vary but in general are about fifteen to twenty percentage points lower than the rest of the classifiers.  Using attribute features only tends to work as well or slightly better than message features, with big drops only occurring in cyclus and jquery, and scala.  Using both sets of features is comparable to only using attribute features.  Variation between data sets is comparable to the percentage bugginess in each training set, which is to be expected.

As encouraging as these initial results are, accuracy may not be the optimal way to view this data; as Table \ref{tab:buggy} shows, the  majority of our training and testing sets are less than 50 \% buggy.  A classifier could concievably classify all commits as clean, achieve > 50\% accuracy and be of no actual use finding buggy commits. In several instances, this is in fact what happens. The 93.3 \% accuracy seen by jedit is more than a little misleading; the jedit test set is only 6.7\% buggy, and so the jedit classifiers simply guess clean for every instance. This is the case for the majority of message-only feature classifiers; only cyclus and jquery  message-only classifiers ever classify any test commits as buggy.  The results from cyclus and jquery are still promisingly higher than our baseline, which leads us to believe that our features do have some non-random correlation with clean and buggy commits.   All of our attribute-trained and attribute/message-trained classifiers have non-trivial decision boundaries.  To get a better idea of how well our classifiers actually are at correctly predicting commits as buggy, we examine precision/recall graphs for cyclus, scala, and scipy by varying the ensemble classifier threshold from 0.0\% agreement (always classify buggy) to 100\% agreement in 10\% increments.  Precision (True Positives/(True Positives+False Positives) and Recall (True Positives/(True Positives+False Negatives)) seem like much more natural fits to analyze how well our ensemble classifiers are at classifying buggy commits.  We define buggy to be a positive and clean to be a negative. Intuitively, the farther up and to the right a point is, the better it performs at finding only true positives. We also provide some F-measure scores for the classifiers at various thresholds; the F-measure is the harmonic mean of precision and recall.  Assuming precision and recall are equally valued, a higher F-measure is an indication of better performance.

\begin{figure}[H]%
\centering
\subfloat[Cyclus]{\includegraphics[width=0.5\textwidth]{images/cyclus_pr_ann}}\hfill%
\subfloat[Scala]{\includegraphics[width=0.5\textwidth]{images/scala_pr_ann}}\\
\subfloat[Scipy]{\includegraphics[width=0.5\textwidth]{images/scipy_pr_ann}}\hfill
\subfloat[Cyclus - ROC graph]{\includegraphics[width=0.5\textwidth]{images/cyclus_roc}}\hfill

@@

As these figures show, using only comments can perform better than random, though not always without tuning of the threshold value.  While at the default 50\% threshold, Cyclus has a lower F-measure value than the random weighted coin, the threshold can can be tweaked to perform better. Scala performs better than average by default using message features than the random weighted coin. At the same time, using just comments performs noticeably worse in all cases than using attribute data.  In every case we examined, attribute data outperforms comment data at all thresholds. Using attribute data performs about as well as training on both attribute and comment features, though attribute-only classifiers consistently contained the maximum F-measure.  These results leads us to several conclusions.  First, both sets of attribute and comment features are more predictive than random.  Comparatively, attribute features are a much better approximation of a commit then comment features.  Combining attribute and comment features provide  little additional performance benefit over simply using attributes; with our current set of features, we gain do not gain substantive information from message features we did not already know from attribute features.

@@

A year of repository data before being able to use a tool seems like a high price of admission.  Being able to substitute another repository’s history for your own with little to no hit in performance would make a bug prediction tool more applicable.  Furthermore, what does this say about commits if commits from two unrelated repositories are similar enough that one can be used to train the other?  To answer these questions, we decided to  scipy and git to train our classifier and test on the other repositories.  Scipy and git were chosen because they were large repositories with good performance and non trivial decision boundaries.  In order for training and testing data to be compatible, the user feature had to be removed from all data sets.

@@

\addcontentsline{toc}{section}{Bibliography}
\begin{thebibliography}{99}
\end{thebibliography}

>>>>

\usepackage{epigraph}
\usepackage{url}

@@

\usepackage{etoolbox}
\makeatletter
\patchcmd{\epigraph}{\@epitext{#1}}{\itshape\@epitext{#1}}{}{}
\makeatother\usepackage{algorithm}
\usepackage{multirow}
\usepackage{algpseudocode}
\begin{document}
% generates the title
\bibliographystyle{acm}

\begin{titlepage}
\begin{center}

@@

\begin{abstract}
On a given day, a large open-source Git Repository likely receives many pull requests, plenty of which are submitted by “untrusted” public members who have yet to contribute to the repository. With so much information to look up and code to test for managers of the repository, we have developed a method to extract metadata about commits and their messages, analyze this data using machine learning techniques, and determine which commits are suspect for introducing new bug(s). The accuracy of our classification method is verified using a number of open-source git repositories, including jedit, jquery, scala, and git itself. Our ensemble classifier correctly predicts bugginess of commits between 70 and 90\% of the time, outperforming the baseline of random weighted guessing by15 to 25\%. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about suspect commits and also seeks to inform contributors in ways to improve their commit structure to make their commits less suspected.
\end{abstract}

@@

In this paper, we discuss our development of a model which attempts to predict the bugginess of commits submitted to a repository by using machine-learning techniques trained on attributes of the commits and their messages. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about which commits are most likely to be buggy, and it does so without any analysis of the code which is being committed.

Furthermore, a beneficial side-effect of our examination of commit attributes and commit message attributes is some prescriptive advice for future contributors to repositories. Examination of the information gain to our learner allowed us to see which attributes of commits were the most correlated with buggy commits, implying that perhaps contributors should alter the way they commit to avoid these attributes.

The next section frames this project with the related work of others. Section \ref{approach} discusses our approach in developing our model including data sources, feature selection, and algorithm development. Section \ref{results} discusses the refinement of the model, presents our results, and discusses our methodology for the validation of our results. Section \ref{threats} discusses shortcomings and threats to validity, section \ref{future} discusses future work, and section \ref{conclude} concludes the paper.

\section{Related Work}
Using version control system history to aid the development process is not a new idea; the wealth of data that repositories store makes them very attractive artifacts to researchers who want to understand and improve the ways in which code is written. In the last ten years a good deal of work has gone into trying to use repository data to make various aspects of the development process easier ~\cite{Kagdi:2007:STA:1345056.1345057}. In the early 2000’s, Zimmerman et al. ~\cite{zimmermann-icse-2004} and Ying ~\cite{Ying:2004:PSC:1018037.1018388} developed systems to mine version history to make suggestions on potential locations for changes based on recent alterations to versioned files.Their results were very interesting, reliably finding associations between sections of code and between code and documentation.

A common goal in many projects involving software repositories is attempting to predict the bugginess of future code using some set of metrics. A wide variety of metrics have been researched, including code churn ~\cite{Nagappan:1062514}, association of changed files ~\cite{zimmermann-icse-2004}, distance between team members ~\cite{Cataldo:2011:FLI:1985793.1985816}, and commit size ~\cite{Hindle:2008:LCT:1370750.1370773}. Recent research has also been done to analyze the accuracy of predicting one repository’s future defects using a different repository’s past history ~\cite{Zimmermann:2009:CDP:1595696.1595713}. Work has also been done on analyzing characteristics of bugs and bug fixes ~\cite{Zimmermann:2012:CPB:2337223.2337363}.

There has also been some work in attempting to automatically infer which past commit introduced a bug. Originally described in ~\cite{Sliwerski:2005:CIF:1082983.1083147}, the SZZ algorithm uses keywords to find bug fixes, and then uses the version system’s blame feature to find which commits last touched the code this bug fix attempted to fix. Future improvements were also made by ~\cite{Kim:2006:AIB:1169218.1169308}, which we discuss in detail later.

Some work has also been done by this group at attempting to use machine learning techniques to predict the bugginess of future commits ~\cite{Kim:2008:CSC:1399105.1399451}. Our work differs from theirs in several ways, namely that their work focuses more heavily on analysis of committed code, which we generally ignore in favor of the simple attributes and message structure of a commit.  Superficially, their work was on Subversion projects while ours were on git projects.      
\section{Approach}
\label{approach}
\subsection{Mining Git Repositories}
We mined eight open-source repositories hosted on Github.com for features to serve as our testing data sets, and these can be seen in Table \ref{tab:repos}. The repositories are quite varied; they range in size from around 2000-30000 commits and in age from roughly 3-13 years. The repositories also vary considerably in their goals — they include a programming language, a versioning control system, and a nuclear fuel cycle simulator. We extracted two sets of features about commits from each repository: commit attributes and message attributes. Commit attributes are information about a commit excluding actual analysis of the code or the commit message. Examples of commit attributes we extracted are the number of lines added, the number of lines removed, the contributor, the length of the comment, the day of the week of the commit, and the number of files altered. The commit message attributes we selected are the frequency of words, grammatical correctness, and readability and stylistic metrics of the message. We used the Flesch-Kincaid measure for readability ~\cite{Flesch} , diction, a unix command line tool, to quantify style (triteness, over-wordiness), and Queequeg to test the degree of grammatical correctness ~\cite{Queequeg} for each commit message. Our analysis of the commit messages assumes they are written in English. A complete list of the attributes we examined can be found in Table \ref{tab:attribs}.

\subsection{Automatically Classifying Past Commits}
To create a classification model from these features, we require a ground truth about whether or not each commit was bug inducing. We used a modified version of the SZZ algorithm from ~\cite{Sliwerski:2005:CIF:1082983.1083147} to determine the set of commits for each repository that were bug inducing. This technique works by first identifying the set of commits in the repository which are bug fixes. Our modification of the algorithm accomplishes this with an analysis of the commit message looking either for words such as “bug” or “fix” or for strings of numbers and letters that appear to be bug-tracking numbers. After defining this set of bug fix commits, we process each commit individually, identifying sections of source code, called hunks, that the commit altered. For each hunk, we then flag as bug inducing the most-recent commit before the bug fix commit which altered that hunk of code. This analysis is conducted using an annotation graph search. Obviously, this heuristic is imperfect; it depends on bug fix commits being atomic and on bugs being discovered and fixed immediately after their introduction. However, as Kim et. al showed in ~\cite{Kim:2006:AIB:1169218.1169308}, this technique tends to work well in practice, as their study using actual developers to confirm bugginess found only a 4-5\% rate of false positives. This algorithm works well in practice and serves as a good estimation for which commits are bug inducing, so we adopted it.

\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |}
    \hline
    Repository & Startdate & $\#$  Commits & $\#$ Buggy  Commits & \% Buggy \\ \hline
    one     & June 2008   &   8179 & 2744 & 33.6 \\ \hline
    cyclus & March 2010 &  2162 & 1071 & 49.5 \\ \hline
    git        & April 2005    &   28788 & 10682 & 37.1 \\ \hline
    jedit & Sept 1998 &  6890 & 3190 & 46.3 \\ \hline
    jquery     & March 2006   &   5608 & 3074 & 54.8 \\ \hline
    puppet & April 2005 &  12174 & 4812 & 39.5 \\ \hline
    scala     & Feb 2003   &   20398 & 9584 & 47.0 \\ \hline
    scipy & Feb 2001 &  10035 & 3252 & 32.4 \\ \hline        	
    \end{tabular}
\end{center}\caption{Mined Repositories}
\label{tab:repos}
\end{table}

@@

\subsection{Machine Learning Algorithms}
With features extracted and a bugginess classification in hand for each commit for our selected repositories, we have the input prepared for constructing, training, and validating a machine-learning algorithm. After some experimentation with individual classifiers, the method we selected to predict bugginess is an ensemble classifier, which aggregates the outputs of several machine-learning classifiers, which can be found in Table ~\ref{algs}. Ensemble classifiers generally provide more accurate and consistent results than a single classifier because, assuming the individual classifiers are searching different parts of the hypothesis space, the likelihood of a majority of classifiers being wrong is less likely than a single classifier being incorrect. An added benefit of using an ensemble classifier is it easily allows the user to specify a confidence value for classifying commits as buggy; the more classifiers in agreement, the higher the confidence. Unless otherwise stated our results take the simple majority of the classifications returned.

\begin{table}
\begin{center}
    \begin{tabular}{ | c | }
    \hline

weka.classifiers.trees.J48\\ \hline
weka.classifiers.bayes.NaiveBayes\\ \hline
weka.classifiers.functions.SMO\\ \hline
weka.classifiers.bayes.BayesNet\\ \hline
weka.classifiers.functions.MultilayerPerceptron\\ \hline
weka.classifiers.meta.Bagging\\ \hline
weka.classifiers.meta.ClassificationViaClustering\\ \hline
weka.classifiers.meta.RandomSubSpace\\ \hline
weka.classifiers.rules.ConjunctiveRule\\ \hline
weka.classifiers.rules.DecisionTable\\ \hline
weka.classifiers.trees.DecisionStump\\ \hline
weka.classifiers.functions.VotedPerceptron\\ \hline
   weka.classifiers.rules.JRip\\ \hline

    \end{tabular}
\end{center}
\caption{List of Weka classifiers used}
\label{algs}
\end{table}

The simple, obvious solution would be to classify a pull request clean if all commits in it are clean, and buggy otherwise. This seems to be too drastic a measure, however, due to these “oops” commits. Any method for classifying requests should take into account that buggy commits in a pull request can potentially contain the associated bug fix in the same request.  We propose a variation on the SZZ algorithm to handle this possibility. All commits are initially given a label using our ensemble classifier. For a buggy commit in the pull request, we take every hunk from the commit and look forward in time for a clean commit with that hunk.  Finding a hunk in a clean commit would imply that whatever bug originally existed has been fixed.  If all the buggy hunks have corresponding clean hunks later in the pull request, or if the number of unpaired buggy hunks is below some threshold, the pull request is accepted as clean. Unfortunately, due to time constraints we were not able to test the effectiveness of this method.

The features we chose to represent our commits are fairly simple ones; of the commit attribute data we use, only the day of the week required any computation. Most of these attributes are presented to the user by git when they make a commit. We did some initial testing with a decision tree classifier, inspecting changes in results while testing different subsets of features.  We also manually kept track of which features were pruned from the tree, which indicates they are less informative. We concluded time and date commit data is not very informative for the open source projects we chose to study. Year and Month are too large to contain much signal, and day of month and minute are too specific. Because hour is not stored in local time and the generally distributed nature of these projects, we did not find hour to be an informative feature. It is possible that these features could be more valuable in a highly centralized development structure, where there is extra knowledge of development schedules, but without any additional knowledge, we decided to ignore specific time-date data.

s
\subsection{Testing Methodology}

To test the effectiveness of our feature selection, we mined features from eight open source repositories. We attempted to choose projects with different life spans and applications to make our results more generalizable.  The list of projects mined, their number of commits, and the percentage of those commits we found to be buggy are in table \ref{tab:repos}.

For each repository we mined, we took the year of 2013, regardless of its size, to be our test set. The reasoning behind this is that in practice, users will want to classify new commits as they come in, and the most recent year of commits were the best fit of the data we had. Notice due to the way our heuristic works (start at a bug fix and work back) our test set is likely to contain more false negatives because the bug fixes have potentially not been written yet. However, in practice this will also be the case, so we feel this should not unreasonably skew our results.
 \begin{figure}
\centering
	\includegraphics[width=0.6\textwidth]{images/history}
\caption{Testing and Training Sets}
\label{git_comp}

\end{figure}
\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |c|}
    \hline
Repo & Test Set & 6Mo Train  & 1 Yr Train   & 2 Yr Train & All Train \\ \hline
one &  2304  &  1190 &  2423 & 4367  &  5874 \\ \hline
cyclus & 546  & 389  & 1231  & 1524  & 1616 \\ \hline
git & 2916  & 1369  & 2630  & 5129  & 25869 \\ \hline
jedit & 165  & 301  & 760  & 1401  & 6725 \\ \hline
jquery & 898  & 592  & 925  & 1934  & 4695 \\ \hline
puppet & 2195  & 980  & 2130  & 3854  & 9979 \\ \hline
scala & 1752  & 1347  & 2983  & 5080  & 18644 \\ \hline
scipy & 1873  & 546  & 1130  & 1786  & 8162 \\ \hline
\end{tabular}
\end{center}\caption{Size of Training and Test Sets}
\label{tab:size}
\end{table}

\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |c|}
    \hline    
Repo & Test Set & 6Mo Train  & 1 Yr Train   & 2 Yr Train & All Train \\ \hline
one  & 23.1 & 26.4 & 30.2 & 35.4 & 37.7 \\ \hline 
cyclus  & 30.6 & 44.4 & 50.6 & 54.9 & 55.9 \\ \hline 
git  & 13.9 & 22.1 & 22.5 & 23.4 & 39.7 \\ \hline
jedit  & 6.7 & 13.9 & 24.7 & 23.1 & 47.3 \\ \hline
jquery  & 35.7 & 43.2 & 46.6 & 53.9 & 58.6 \\ \hline 
puppet  & 18.7 & 20.0 & 26.1 & 29.1 & 44.1 \\ \hline 
scala  & 27.2 & 45.3 & 48.8 & 50.3 & 48.9 \\ \hline 
scipy  & 18.8 & 23.6 & 23.6 & 24.7 & 35.5 \\ \hline
\end{tabular}
\end{center}\caption{Percent Bugginess of Training and Test Sets}
\label{tab:buggy}
\end{table}

\begin{figure}%
\centering
\subfloat[Git]{\includegraphics[width=0.5\textwidth]{images/perc_buggy_git}}\hfill%
\subfloat[Puppet]{\includegraphics[width=0.5\textwidth]{images/perc_buggy_puppet}}
\caption{Percent Buggy Commits over Time}
\end{figure}

For sets of training data, we took commits from the final day of 2012 back six months, one year, two years, and to the start of the repository. The goal here is to see how our results change with more data to train on (and potentially overfit to). Tables \ref{tab:size} and \ref{tab:buggy} show the size and percentage of commits which are buggy, respectively. Notice that as time increases, the percentage of buggy commits increases (excepting scala all time). This seems to be an artifact of our heuristic; older bugs are more likely to have associated bug fixes, and so are more likely to be found by our method. Without having the actual distribution of buggy commits, we can make no assumptions about its trend over time.

To compare our features against some baseline, we created a “random weighted coin” classifier which calculated the percent buggy in a training set and used this percentage as the weight on a random buggy/clean coin for each test instance. We feel this represents a better floor against which to compare our results than simply using a fair coin. All discussion of random coin results are the average of 100 trials. To compare the effectiveness of attribute and message features, we also trained classifiers using only attribute features, only message features, and both sets of features.

@@

Figure \ref{git_comp} contains our accuracy results of every mined repository using one year of training data. Results for random weighted coin vary but in general are about fifteen to twenty percentage points lower than the rest of the classifiers. Using attribute features only tends to work as well or slightly better than message features, with big drops only occurring in cyclus, jquery, and scala. Using both sets of features is comparable to only using attribute features.  Variation between data sets is comparable to the percentage bugginess in each training set, which is to be expected.

 \begin{figure}[h]
\centering
	\includegraphics[width=0.8\textwidth,height=.4\textwidth]{images/learner_comp}
\caption{Comparison of Feature Results - 1 Year}
\label{git_comp}

\end{figure}
As encouraging as these initial results are, accuracy may not be the optimal way to view this data; as Table \ref{tab:buggy} shows, the  majority of our training and testing sets are less than 50 \% buggy.  A classifier could concievably classify all commits as clean, achieve > 50\% accuracy, and be of no actual use in predicting buggy commits. In several instances, this is in fact what happens. The 93.3 \% accuracy seen by jedit is more than a little misleading; the jedit test set is only 6.7\% buggy, and so the jedit classifiers simply guess clean for every instance. This is the case for the majority of message-only feature classifiers; only cyclus and jquery  message-only classifiers ever classify any test commits as buggy. The results from cyclus and jquery are still promisingly higher than our baseline, which leads us to believe that our features do have some non-random correlation with clean and buggy commits. All of our attribute-trained and attribute/message-trained classifiers have non-trivial decision boundaries. To get a better idea of how well our classifiers actually are at correctly predicting commits as buggy, we examine precision/recall graphs for cyclus, scala, and scipy by varying the ensemble classifier threshold from 0.0\% agreement (always classify buggy) to 100\% agreement in 10\% increments. Precision (True Positives/(True Positives+False Positives) and Recall (True Positives/(True Positives+False Negatives)) seem like much more natural fits to analyze how well our ensemble classifiers are at classifying buggy commits. We define buggy to be a positive and clean to be a negative. Intuitively, the farther up and to the right a point is, the better it performs at finding only true positives. We also provide some F-measure scores for the classifiers at various thresholds; the F-measure is the harmonic mean of precision and recall.  Assuming precision and recall are equally valued, a higher F-measure is an indication of better performance.

\begin{figure}[h]%
\centering
\subfloat[Cyclus]{\includegraphics[width=0.5\textwidth]{images/cyclus_pr_ann}}\hfill%
\subfloat[Scala]{\includegraphics[width=0.5\textwidth]{images/scala_pr_ann}}\\
\subfloat[Scipy]{\includegraphics[width=0.5\textwidth]{images/scipy_pr_ann}}\hfill
\subfloat[Cyclus - ROC graph]{\includegraphics[width=0.5\textwidth]{images/cyclus_roc}}\hfill

@@

As these figures show, using only comments can perform better than random, though not always without tuning of the threshold value. While at the default 50\% threshold, Cyclus has a lower F-measure value than the random weighted coin; the threshold can can be tweaked to perform better. Scala performs better than average by default using message features than the random weighted coin. At the same time, using just comments performs noticeably worse in all cases than using attribute data. In every case we examined, attribute data outperforms comment data at all thresholds. Using attribute data performs about as well as training on both attribute and comment features, though attribute-only classifiers consistently contained the maximum F-measure. These results leads us to several conclusions. First, both sets of attribute and comment features are more predictive than random. Comparatively, attribute features are a much better approximation of a commit then comment features. Combining attribute and comment features provide little additional performance benefit over simply using attributes; with our current set of features, we do not gain substantive information from message features we did not already know from attribute features.

@@

A year of repository data before being able to use a tool seems like a high price of admission.  Being able to substitute another repository’s history for your own with little to no performance cost would make a bug prediction tool more applicable. Furthermore, what does this say about commits if commits from two unrelated repositories are similar enough that one can be used to train the other? To answer these questions, we decided to use scipy and git to train our classifier and test on the other repositories. Scipy and git were chosen because they were large repositories with good performance and non-trivial decision boundaries. In order for training and testing data to be compatible, the user feature had to be removed from all data sets.

@@

\bibliography{Master}
